Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review

### 2022-01-13 _bookdown_files/08-appendix.Rmd
Inclusion of PRISMA checklist
Cross-reference issue fixed
Complete draft

@@

### A. Reference tables

@@

#### List of references included in the review

@@

@@

Chandler, Cristian J., Bukowski, L.A.,
Matthews, D.D., Hawk, M.E., Markovic, N., Egan, J.E., Stall, R.D., 2020a.
Examining the Impact of a Psychosocial Syndemic on Past Six-Month HIV Screening
Behavior of Black Men who have Sex with Men in the United States: Results from
the POWER Study. AIDS Behav 28, 428--436.
<https://doi.org/10.1007/s10461-019-02458-z>

Chandler, Cristian J., Bukowski, L.A.,
Matthews, D.D., Hawk, M.E., Markovic, N., Stall, R.D., Egan, J.E., 2020b.
Understanding the impact of a syndemic on the use of pre-exposure prophylaxis
in a community-based sample of behaviorally PrEP-eligible BMSM in the United
States. AIDS Care 32, 551--556. <https://doi.org/10.1080/09540121.2019.1659921>

Chandler, Cristian J, Meunier, E., Eaton,
L.A., Andrade, E., Bukowski, L.A., Matthews, D.D., Raymond, H.F., Stall, R.D.,
Friedman, M.R., 2020. Syndemic health disparities and sexually transmitted
infection burden among black men who have sex with men engaged in sex work in
the u.S. Arch Sex Behav. <https://doi.org/10.1007/s10508-020-01828-2>

@@

Dyer, T.V., Turpin, R.E., Stall, R., Khan,
M.R., Nelson, L.E., Brewer, R., Friedman, M.R., Mimiaga, M.J., Cook, R.L., O'Cleirigh,
C., Mayer, K.H., 2020. Latent Profile Analysis of a Syndemic of Vulnerability
Factors on Incident Sexually Transmitted Infection in a Cohort of Black Men Who
Have Sex With Men Only and Black Men Who Have Sex With Men and Women in the HIV
Prevention Trials Network 061 Study. Sex Transm Dis 47, 571--579.
<https://doi.org/10.1097/OLQ.0000000000001208>

@@

Lee, J S, Bainter, S.A., Carrico, A.W.,
Glynn, T.R., Rogers, B.G., Albright, C., O'Cleirigh, C., Mayer, K.H., Safren,
S.A., 2020. Connecting the dots: a comparison of network analysis and
exploratory factor analysis to examine psychosocial syndemic indicators among
HIV-negative sexual minority men. J Behav Med.
<https://doi.org/10.1007/s10865-020-00148-z>

Lee, Jasper S., Safren, S.A., Bainter,
S.A., Rodríguez-Díaz, C.E., Horvath, K.J., Blashill, A.J., 2020. Examining a
Syndemics Network Among Young Latino Men Who Have Sex with Men. Int J Behav Med
27, 39--51. <https://doi.org/10.1007/s12529-019-09831-1>

@@

@@

Moeller, R.W., Halkitis, P.N., Surrence,
K., n.d. The interplay of syndemic production and serosorting in drug-using gay
and bisexual men. J. Gay Lesbian Soc. Serv 23, 89--106.
<https://doi.org/10.1080/10538720.2010.538007>

@@

@@

@@

### B. Measurement tables

>>>>

## A. PRISMA-ScR checklist

```{r PRISMA-ScR, tab.id = "PRISMA-ScR", echo=FALSE, message= FALSE,warning=FALSE}
source("./scripts/supplementary_tables/PRISMA-ScR.R", local = knitr::knit_global())

.PRISMA_ft

@@

## B. Reference tables

@@

### List of references included in the review

@@

Bulled, N., 2021. A new approach to measuring the synergy in a syndemic: Revisiting the SAVA syndemic among urban MSM in the United States. Glob Public Health 1--11. <https://doi.org/10.1080/17441692.2021.1974513>

@@

Chandler, C.J., Bukowski, L.A., Matthews, D.D., Hawk, M.E., Markovic, N., Egan, J.E., Stall, R.D., 2020a. Examining the Impact of a Psychosocial Syndemic on Past Six-Month HIV Screening Behavior of Black Men who have Sex with Men in the United States: Results from the POWER Study. AIDS Behav 28, 428--436. <https://doi.org/10.1007/s10461-019-02458-z>

Chandler, C.J., Bukowski, L.A., Matthews, D.D., Hawk, M.E., Markovic, N., Stall, R.D., Egan, J.E., 2020b. Understanding the impact of a syndemic on the use of pre-exposure prophylaxis in a community-based sample of behaviorally PrEP-eligible BMSM in the United States. AIDS Care 32, 551--556. <https://doi.org/10.1080/09540121.2019.1659921>

Chandler, C.J., Meunier, É., Eaton, L.A., Andrade, E., Bukowski, L.A., Matthews, D.D., Raymond, H.F., Stall, R.D., Friedman, M.R., 2021. Syndemic Health Disparities and Sexually Transmitted Infection Burden Among Black Men Who Have Sex with Men Engaged in Sex Work in the U.S. Arch Sex Behav 50, 1627--1640. <https://doi.org/10.1007/s10508-020-01828-2>

Chuang, D.-M., Newman, P.A., Fang, L., Lai, M.-C., 2021. Syndemic Conditions, Sexual Risk Behavior, and HIV Infection Among Men Who Have Sex with Men in Taiwan. AIDS BEHAV 25, 3503--3518. <https://doi.org/10.1007/s10461-021-03269-x>

@@

Dyer, T.V., Turpin, R.E., Stall, R., Khan, M.R., Nelson, L.E., Brewer, R., Friedman, M.R., Mimiaga, M.J., Cook, R.L., O'Cleirigh, C., Mayer, K.H., 2020. Latent Profile Analysis of a Syndemic of Vulnerability Factors on Incident Sexually Transmitted Infection in a Cohort of Black Men Who Have Sex With Men Only and Black Men Who Have Sex With Men and Women in the HIV Prevention Trials Network 061 Study. Sexually Transmitted Diseases 47, 571--579. <https://doi.org/10.1097/olq.0000000000001208>

@@

Leblanc, N.M., Crean, H.F., Dyer, T.P., Zhang, C., Turpin, R., Zhang, N., Smith, M.D.R., McMahon, J., Nelson, L., 2021. Ecological and Syndemic Predictors of Drug Use During Sex and Transactional Sex among U.S. Black Men Who Have Sex with Men: A Secondary Data Analysis from the HPTN 061 Study. Arch Sex Behav, Erratum in: Arch Sex Behav. 2021 May 11;:; PMID: 33974202 [[https://www.ncbi.nlm.nih.gov/pubmed/33974202]](https://www.ncbi.nlm.nih.gov/pubmed/33974202]) 50, 2031--2047. <https://doi.org/10.1007/s10508-020-01871-z>

Lee, J.S., Bainter, S.A., Carrico, A.W., Glynn, T.R., Rogers, B.G., Albright, C., O'Cleirigh, C., Mayer, K.H., Safren, S.A., 2020a. Connecting the dots: a comparison of network analysis and exploratory factor analysis to examine psychosocial syndemic indicators among HIV-negative sexual minority men. J Behav Med. <https://doi.org/10.1007/s10865-020-00148-z>

Lee, J.S., Safren, S.A., Bainter, S.A., Rodríguez-Díaz, C.E., Horvath, K.J., Blashill, A.J., 2020b. Examining a Syndemics Network Among Young Latino Men Who Have Sex with Men. Int J Behav Med 27, 39--51. <https://doi.org/10.1007/s12529-019-09831-1>

@@

Mimiaga, M.J., Hughto, J.M.W., Klasko-Foster, L., Jin, H., Mayer, K.H., Safren, S.A., Biello, K.B., 2021. Substance Use, Mental Health Problems, and Physical and Sexual Violence Additively Increase HIV Risk Between Male Sex Workers and Their Male Clients in Northeastern United States. J Acquir Immune Defic Syndr 86, 305--312. <https://doi.org/10.1097/QAI.0000000000002563>

@@

Moeller, R.W., Halkitis, P.N., Surrence, K., 2011. The interplay of syndemic production and serosorting in drug-using gay and bisexual men. J. Gay Lesbian Soc. Serv 23, 89--106. <https://doi.org/10.1080/10538720.2010.538007>

@@

Satyanarayana, S., Safren, S.A., Rogers, B.G., Bainter, S.A., Christopoulos, K.A., Fredericksen, R.J., Mathews, W.C., Moore, R.D., Mugavero, M.J., Napravnik, S., Carrico, A.W., Mimiaga, M.J., Mayer, K.H., Crane, H.M., 2021. Estimating HIV transmissions in a large U.S. clinic-based sample: effects of time and syndemic conditions. J Int AIDS Soc 24, e25679. <https://doi.org/10.1002/jia2.25679>

@@

Tapia, G.R., Glynn, T.R., Miller, C., Manuzak, J.A., Broedlow, C.A., Mcgaugh, A., Cherenack, E.M., Bauermeister, J.A., Grov, C., Dilworth, S.E., Parisi, R., Martinez, D., Klatt, N.R., Carrico, A.W., 2021. Syndemics and preexposure prophylaxis are independently associated with rectal immune dysregulation in sexual minority men. AIDS 35, 1295--1300. <https://doi.org/10.1097/QAD.0000000000002866>

@@

## C. Measurement tables

### 2022-01-13 _bookdown_files/index.Rmd
Complete draft

---
title: "Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review"
author: 
- "Maxence R. Ouafik^1^, Laetitia Buret^2^, Jean-Luc Belche^3^, Beatrice Scholtes^4^"
- "^1^ Corresponding author at : General Practice Department - Primary Care and Health Research Unit, MD - PhD student,  University of Liège, Liège, Belgium <maxence.ouafik@uliege.be> ; Quartier Hôpital B23 Avenue Hippocrate 13 4000 Liège ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-9795-5721"
- "^2^ General Practice Department - Primary Care and Health Research Unit, MD - GP - PhD, research assistant, University of Liège, Liège, Belgium <laetitia.buret@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-6039-9824"
- "^3^ General Practice Department - Primary Care and Health Research Unit, MD - GP - PhD, lecturer, University of Liège, Liège, Belgium <jlbelche@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-8807-0473"
- "^4^ General Practice Department - Primary Care and Health Research Unit, Postdoctoral Researcher,  University of Liège, Liège, Belgium <beatrice.scholtes@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-5274-822X"

>>>>

---
title: "Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review"
author: 
- "Maxence R. Ouafik^1^, Laetitia Buret^2^, Jean-Luc Belche^3^, Beatrice Scholtes^4^"
- "^1^ Research Unit of Primary Care and Health, General Practice Department University of Liège, Liège, Belgium ; Quartier Hôpital B23 Avenue Hippocrate 13, 4000, Liège <maxence.ouafik@uliege.be> ; Quartier Hôpital B23 Avenue Hippocrate 13 4000 Liège ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-9795-5721"
- "^2^ <laetitia.buret@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-6039-9824"
- "^3^  <jlbelche@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-8807-0473"
- "^4^  <beatrice.scholtes@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-5274-822X"
- "*corresponding author: maxence.ouafik@uliege.be https://orcid.org/0000-0002-9795-5721"
